Appendix part 2

### 2025-11-06 Output/authoritarian_only_pdf_pop_rev.Rmd
Cuts and re-ordering in theory section

Theories in the 'regime-weakness' view of electoral manipulation are built on several assumptions about the nature of protest and the information conveyed by the incumbent's vote-share and manipulation efforts. Updating some of these assumptions, I argue, provides a model that more accurately reflects contemporary research on manipulation *and* makes distinct empirical predictions. Each of these assumptions, and how they are adjusted in the 'regime-strength' model of manipulation, is discussed below.

@@

The central argument of this manuscript is that, in authoritarian regimes, incumbents who develop the tools necessary to manipulate elections extensively will also have the tools necessary to quickly prevail over protest movements. This proposition builds off Simpser's foundational argument that manipulated elections can send costly signals of the incumbent's "capacities, resources, [and] dispositions" that will help it retain power in the future [@simpser2013, p. 80]---that is, of its political strength. However, I depart from Simpser in two ways. First, by incorporating more recent research on the principal-agent dynamics inherent in election manipulation, I argue that incumbents who can produce large amounts of election manipulation necessarily have "capacities, resources and dispositions" helpful for defeating protests. This research trend emphasizes the degree to which political principals require the cooperation of large numbers of front-line agents in order to generate extensive election fraud, agents who may shirk if their perceived interests are not aligned with the incumbent [@rundlett2016deliver]. Second, mine is not a signalling argument; good manipulators are likely to have deeper wells of strength than weaker manipulators, whether those resources are successfully signaled to opposition actors or no.

Electoral manipulation has been shown to be more extensive under conditions that minimize principal-agent problems between low-level agents and the incumbent. These include: greater local popularity for the incumbent [@rundlett2016deliver], greater incumbent control over patronage resources [@Harvey2019;@hale_patronal_2014], and lower risk of punishment for pro-regime lawbreaking [@Harvey2022]. Lastly, extensive manipulation also indicates that large number of agents assess that the incumbent will remain in power in the future [@simpser2013], which itself becomes a self-reinforcing equilibrium [@hale_patronal_2014].

@@

```{=latex}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\begin{tabular}{@{}rll@{}}
\toprule
Incumbent's genuine popularity:       & \multicolumn{2}{c}{Low}  \\ \midrule
\multicolumn{1}{r|}{Protest is assumed to be:}                  & \multicolumn{1}{c|}{Instrumental} & \multicolumn{1}{c|}{Multipurpose} \\ \midrule
\multicolumn{1}{|l|}{Manipulation...} &  & \multicolumn{1}{l|}{} \\ \midrule
\multicolumn{1}{|r|}{...obscures strength / indicates weakness} & \multicolumn{1}{l|}{Increasing}   & \multicolumn{1}{l|}{Increasing}   \\ \midrule
\multicolumn{1}{r|}{...reflects strength}                       & \multicolumn{1}{l|}{Decreasing}   & \multicolumn{1}{l|}{Decreasing}   \\ \bottomrule
\end{tabular}
\caption{Expected relationship between protest duration and increasing election manipulation}
\label{tab:duration}
\end{table}
```

How, then, would this view of electoral manipulation map onto the instrumental vs. multipurpose views of protest discussed above? While regime-weakness models have exclusively (to my knowledge) been framed around protest initiation, it is straightforward to extend their predictions to protest duration. Regime-weakness models of electoral manipulation treat election manipulation and genuine votes as substitute goods. For any given vote-share, an increase in manufactured votes reduces the number of genuine votes; that is, the higher the number of manufactured votes for any given vote total, the lower the incumbent's genuine popularity is and the less likely they are to survive a challenge. In an instrumental mode of protest, strategic opposition actors perceive the incumbent's relative lack of popularity, and count on the majority of the public to back their challenge. Increasing manipulation indicates deeper unpopularity (holding vote-share constant), so we should expect a less popular incumbent to fail more quickly. The same logic holds, with slightly different mechanisms, if protests are assumed to be multipurpose. Here, greater manipulation is used to overcome deeper unpopularity (i.e. widespread grievances); more manipulation indicates an incumbent facing an increasingly powerful challenger. Thus, the regime-weakness model of manipulation should predict that the duration of unsuccessful protests will be increasing in election manipulation: more manipulation indicates a stronger challenger, which will take longer to defeat on average.

For the regime-strength model of manipulation, the opposite relationship is expected, as laid out above. Comparing Table \@ref(tab:duration) and \@ref(tab:initiation) shows that the hypotheses generated by the preferred model--one in which manipulation indicates strength and protest is multipurpose are distinct from those in other quadrants.

@@

Both models of election manipulation consider genuine popularity to be a source of regime strength, and assume that increasing electoral manipulation either distorts or weakens this indicator by mingling genuine votes with manufactured ones. The distinction between the two models is over whether or not manipulation simultaneously indicates additional sources of strength other than popularity.

>>>>

Considering how electoral manipulation may be tied to protest duration under the regime-weakness and regime-strength models reveals distinct predictions. Specifically, as discussed below, protest duration should decrease with manipulation in the regime-weakness model, but increase in the regime-strength model (conditional on incumbent vote-share). The logic discussed below hinges on the assumption that, on average, authoritarian governments will seek to quash protest movements quickly once they appear. How plausible is this assumption?

@@

## The regime-strength theory of manipulation and protest duration

The central argument of this manuscript is that, in authoritarian regimes, incumbents who develop the tools necessary to manipulate elections extensively will also have the tools necessary to more quickly prevail over protest movements. This proposition builds off Simpser's foundational argument that manipulated elections can send costly signals of the incumbent's "capacities, resources, [and] dispositions" that will help it retain power in the future [@simpser2013, p. 80]---that is, of its political strength. However, I depart from Simpser in two ways. First, by incorporating more recent research on the principal-agent dynamics inherent in election manipulation, I argue that incumbents who can produce large amounts of election manipulation necessarily have "capacities, resources and dispositions" helpful for defeating protests. Second, mine is not a signalling argument; good manipulators are likely to have deeper wells of strength than weaker manipulators, whether those resources are successfully signaled to opposition actors or no.

Recent research emphasizes the degree to which political principals require the cooperation of large numbers of front-line agents in order to generate extensive election fraud, agents who may shirk if their perceived interests are not aligned with the incumbent [@rundlett2016deliver]. Electoral manipulation has been shown to be more extensive under conditions that minimize principal-agent problems between low-level agents and the incumbent. These include: greater local popularity for the incumbent [@rundlett2016deliver], greater incumbent control over patronage resources [@Harvey2019;@hale_patronal_2014], and lower risk of punishment for pro-regime lawbreaking [@Harvey2022]. Lastly, extensive manipulation also indicates that large number of agents assess that the incumbent will remain in power in the future [@simpser2013], which itself becomes a self-reinforcing equilibrium [@hale_patronal_2014].

@@

@@

Still, a full accounting of a regime's strength would include the incumbent's genuine popularity [@Gerschewski2013]. Both models of election manipulation consider genuine popularity to be a source of regime strength, and assume that increasing electoral manipulation either distorts or weakens this indicator by mingling genuine votes with manufactured ones. The distinction between the two models is over whether or not manipulation simultaneously indicates additional sources of strength other than popularity.
